\section{Functional Requirements}
%Describe in a very precise and schematic way (bullet lists):
%Type of information stored
%Operations that different users can execute on such data
The database must store:
\begin{itemize}

    \item \textbf{Biochemical Analysis} data including:
    \begin{itemize}
        \item Operation performed by Clinical Engineers.
        \item List of samples used.
        \item Results.
    \end{itemize}
    
    \item \textbf{Clinical Engineers} data, including:
    \begin{itemize}
        \item Name and surname.
        \item E-mail.
        \item Phone number.
        \item ID (badge number).
        \item Its role in the hospital. 
        \item Its research group name.
    \end{itemize}
    
    \item \textbf{Clinical Study} data, including:
    \begin{itemize}
        \item CSID.
        \item Brief description of the study.
        \item Research team that defined the clinical study.
    \end{itemize}
    
    \item \textbf{Data Scientists} data, including:
    \begin{itemize}
        \item Name and surname.
        \item E-mail.
        \item Phone number.
        \item ID (badge number).
        \item Its role in the hospital.  
        \item Its research group name.
    \end{itemize}

    \item \textbf{Doctors} data, including:
    \begin{itemize}
        \item Name and surname.
        \item E-mail.
        \item Phone number.
        \item ID (badge number).
        \item Its role in the hospital.        
    \end{itemize}
    
    \item \textbf{Medical Appointment} data, including:
    \begin{itemize}
        \item Type of service provided (MAID).
        \item If samples were collected or not.
        \item The doctor performed the medical examination.
        \item The patient that undergoes the medical appointment.
    \end{itemize}
    
    \item \textbf{Patients} data, including:
    \begin{itemize}
        \item Name and surname.
        \item Date of birth.
        \item Sex.
        \item Fiscal code.  
        \item Height.  
        \item Weight.  
        \item Clinical history.
        \item Date of the visits. 
        \item Diagnosis.
        \item Progression of the illness.  
        \item State of the illness.
        \item State of the patient.
        \item Proposed treatment. 
    \end{itemize}

    \item \textbf{Research Team} data, including:
    \begin{itemize}
        \item Name of the group.
        \item Clinical studies of the team.
        \item Clinical Engineers that belong to the group.
        \item Data Scientists that belong to the group.
    \end{itemize}

    \item \textbf{Samples} data, including: 
    \begin{itemize}
        \item UIGID.
        \item Biochemical data.
        \item Storing location.
        \item Availability status. 
    \end{itemize}

    \item \textbf{Statistical Analysis} data, including:
    \begin{itemize}
        \item Methods used by Data Scientists.
        \item Data used.
        \item Results.
    \end{itemize}
    
\end{itemize}
The system must allow:
\begin{itemize}
    \item Doctors, Clinical Engineers, and Data Scientists to log in and sign up, managing different user roles for them.
    \item Doctors to register and update patients' personal and medical information.
    \item Doctor to perform medical appointments for each patient.
    \item Clinical Engineers to label and store samples.
    \item Clinical Engineers perform clinical studies for each sample and update their biochemical data.
    \item Data Scientist to access the biochemical and clinical data of the samples, updating statistical studies.
    \item Researchers (Clinical Engineers and Data Scientists) to create/join a Research Team.
\end{itemize}