\begin{longtable}{|p{.20\columnwidth}|p{.15\columnwidth} |p{.30\columnwidth}|p{.10\columnwidth}|p{.20\columnwidth} |} 
\hline
\textbf{Relation} & \textbf{Attribute} & \textbf{Description} & \textbf{Domain} & \textbf{Constraints} \\\hline

\multirow{2}{*}{Belongs}
% Sample / Group
	& UIGID
		& Unique identifier of the Sample. 
		& Serial
		& Foreign key to Sample, Not NULL, primary key with Study Group ID
\\\cline{2-5}
	& StudyGroupID
		& Unique identifier of the Group to which the Sample belongs.
		& Text
		& Foreign key to Group, Not NULL, primary key with UIGID
\\\hline

\multirow{3}{*}{Clinical Study} 
&CSID 
    &Unique identifier of the Clinical Study. 
    &Text  
    &Primary key
\\\cline{2-5}
&Date 
    &When the Clinical Study has been performed.
    &Date range 
    &Not NULL
\\\cline{2-5}
&Description 
    &The description of the study’s objectives and main features. 
    &Text 
    &
\\\hline

\multirow{3}{*}{Consent} 
&ConsentStatus 
    &It identifies whether the Patient gave or not the Consent for her/his data to be processed.
    &Boolean
    &Not NULL
\\\cline{2-5}
&Purpose 
    &Why the Patient is asked for Consent.
    &Text
    &Not NULL
\\\cline{2-5}
&Duration 
    &Period of time for which the Consent is maintained.
    &Date range
    &Not NULL
    \\\cline{2-5}
&PatientID 
    &ID of the patient giving the consent.
    &Serial
    &Foreign Key to Patient, Not NULL, primary key with CSID
\\\cline{2-5}
&CSID 
    &ID of the clinical study requiring the consent.
    &Text
    &Foreign Key to Clinical Study, Not NULL, primary key with PatientID
\\\hline

\multirow{3}{*}{Defines}
% Research Team / Clinical Study / Research Procedure
	& TeamName 
		& Unique identifier of the Research Team, carrying out the Clinical Study. 
		& Text
		& Foreign key to Research Team, Not NULL, primary key with CSID and Research ID
\\\cline{2-5}
	& CSID 
		& Unique identifier of the Clinical Study. 
		& Text
		& Foreign key to Clinical Study, Not NULL, primary key with Name and Research ID
\\\cline{2-5}
	& ResearchID 
		& Unique identifier of the Research Procedure chosen for the Clinical Study. 
		& Text
		& Foreign key to Research Procedure, Not NULL, primary key with Name and CSID
\\\hline

\multirow{6}{*}{Doctor} 
&ID 
    &Unique identifier of the Doctor.
    &Text
    &Primary key
\\\cline{2-5}
&Name
    &The name of the Doctor
    &Text
    &Not NULL
\\\cline{2-5}
&Surname 
    &The surname of the Doctor.
    &Text
    &Not NULL
\\\cline{2-5}
&Email 
    &The e-mail address of the Doctor.
    &Text
    &Not NULL
\\\cline{2-5}
&Password 
    &The log-in hashed password of the Doctor.
    &Text
    &Not NULL
\\\cline{2-5}
&PhoneNumber 
    &The phone number of the Doctor.
    &Text
    &Not NULL
\\\hline

\multirow{2}{*}{Group} 
&StudyGroupID 
    &Unique identifier of the Group to which the Sample belongs.
    &Text
    &Primary key
\\\cline{2-5}
&KindOfSamples 
    &The type of Sample collected.
    &Text
    &Not NULL
\\\hline

\multirow{4}{*}{Location} 
&StorageID
    &Unique identifier of the Location of the Sample.
    &Text
    &Primary key
\\\cline{2-5}
&Room
    &The room where the Sample is stored.
    &Text
    &Not NULL
\\\cline{2-5}
&Capacity 
    &The number of Sample each Location can contain.
    &Integer
    &Not NULL
\\\cline{2-5}
&Kind 
    &The type of sample storage Location.
    &Text
    &Not NULL
\\\hline

\multirow{2}{*}{Medical Appointment} 
&MAID 
    &Unique identifier of the Medical Appointment.
    &Text
    &Primary key
\\\cline{2-5}
&Date
    &The date when the Medical Appointment has been performed.
    &Date range
    &Not NULL
\\\hline

\multirow{10}{*}{Patient} 
&PatientID 
    &Unique identifier of the Patient.
    &Serial
    &Primary key
\\\cline{2-5}
&Name 
    &The name of the Patient.
    &Text
    &Not NULL
\\\cline{2-5}
&Surname 
    &The surname of the Patient.
    &Text
    &Not NULL
\\\cline{2-5}
&DateOfBirth 
    &The date of birth of the Patient.
    &Date range
    &Not NULL
\\\cline{2-5}
&FiscalCode
    &The fiscal code of the Patient.
    &Text
    &
\\\cline{2-5}
&Height 
    &The height of the Patient.
    &Integer
    &Not NULL
\\\cline{2-5}
&Weight 
    &The weight of the Patient.
    &Integer
    &Not NULL
\\\cline{2-5}
&Sex 
    &The sex of the Patient.
    &Text
    &Not NULL
\\\cline{2-5}
&Status 
    &Identifies if the Patient is sick or healthy.
    &Boolean
    &Not NULL
\\\cline{2-5}
&ClinicalHistory 
    &Description of the Patient's clinical history.
    &Text
    &
\\\cline{2-5}
&ConsentStatus 
    &It identifies whether the Patient gave or not the Consent for her/his data to be processed.
    &Boolean
    &Foreign key to Consent
\\\hline
\newpage
\hline
\multirow{3}{*}{Performs}
% Doctor / Medical Appointment / Patient
	& DoctorID 
		& Unique identifier of the Doctor performing the Medical Appointment. 
		& Text
		& Foreign key to Doctor, Not NULL, primary key with MAID and PatientID
\\\cline{2-5}
	& MAID 	
		& Unique identifier of the Medical Appointment. 
		& Text
		& Foreign key to Medical Appointment, Not NULL, primary key with ID and Patient ID
\\\cline{2-5}
    & PatientID 
    		& Unique identifier of the Patient. 
    		& Serial
    		& Foreign key to Patient, Not NULL, primary key with DoctorID and MAID
\\\hline

\multirow{7}{*}{Research Personnel} 
&ID 
    &Unique identifier of the Research Personnel member.
    &Text
    &Primary key
\\\cline{2-5}
&Name 
    &The name of the Research Personnel member.
    &Text
    &Not NULL
\\\cline{2-5}
&Surname
    &The surname of the Research Personnel member.
    &Text
    &Not NULL
\\\cline{2-5}
&Email
    &The e-mail of the Research Personnel member.
    &Text
    &Not NULL
\\\cline{2-5}
&Password 
    &The log-in hashed password of the Research Personnel member.
    &Text
    &Not NULL
\\\cline{2-5}
&PhoneNumber
    &The phone number of the Research Personnel member.
    &Text
    &Not NULL
\\\cline{2-5}
&Role
    &Identifies whether the Research Personnel member is a Clinical Engineer or a Data Scientist
    &Boolean
    & Not NULL
\\\hline

\multirow{4}{*}{Research Procedure} 
&ResearchID 
    &Unique identifier of the Research Procedure.
    &Text
    &Primary key
\\\cline{2-5}
&Name
    &Identifies the adopted procedure.
    &Text
    &Not NULL
\\\cline{2-5}
&Description 
    &Description of objectives and main features of the adopted Research Procedure
    &Text
    &Not NULL
\\\cline{2-5}
&NeedFor Anonymization 
    &Identifies whether the adopted Research Procedure has to be anonymized or not.
    &Boolean
    &Not NULL
\\\hline

\multirow{2}{*}{Research Team} 
&Name 
    &Unique identifier of the Research Team.
    &Text
    &Primary key
\\\cline{2-5}
&NumberOf Members 
    &The number of members of the Research Team.
    &Integer
    &Not NULL
\\\hline

\newpage
\hline
\multirow{5}{*}{Results} 
&ICDOCode 
    &Unique identifier of the Results.
    &Text
    &Primary key
\\\cline{2-5}
&Mutation 
    &Number of mutation of the Sample.
    &Integer
    &Not NULL
\\\cline{2-5}
&PutativeCopy NumberAlterations
    &Measures the genomics instability.
    &Float
    &Not NULL
\\\cline{2-5}
&ModelAccuracy 
    &Value of the accuracy metric that describes the performance of the statistical model used.
    &Float
    &
\\\cline{2-5}
&ModelLoss 
    &Value of the loss metric of the statistical model used.
    &Float
    &
\\\cline{2-5}
& CSID 
    & Unique identifier of the Clinical Study.
    & Text 
    & Foreign key to Clinical Study, Not NULL, primary key with ICD-O Code.
\\\hline

\multirow{3}{*}{Sample} 
&UIGID 
    &Unique identifier of the Sample.
    &Serial
    &Primary key
\\\cline{2-5}
&Type
    &The type of the Sample.
    &Text
    &Not NULL
\\\cline{2-5}
&AvailabilityStatus 
    &Identifies whether the Sample is available or not.
    &Boolean
    &Not NULL
\\\cline{2-5}
&MAID 
    &Unique identifier of the Medical Appointment. 
    &Text
    &Foreign key to Medical Appointment
\\\cline{2-5}
&StorageID 
    &Unique identifier of the Location of the Sample.
    &Int
    &Foreign key to Location
\\\hline

\multirow{2}{*}{Undergoes}
% Group / Clinical study 
	& StudyGroupID
		& Unique identifier of the Group which undergoes the Clinical Study.
		& Text
		& Foreign key to Group, Not NULL, primary key with CSID
\\\cline{2-5}
	& CSID 
		& Unique identifier of the Clinical Study. 
		& Text
		& Foreign key to Clinical Study, Not NULL, primary key with Study Group ID
\\\hline

\multirow{2}{*}{Works-in}
% Research Personnel / Research Team
	& ResID 
		& Unique identifier of the Research Personnel member who works in the Research Team. 
		& Text
		& Foreign key to Research Personnel, Not NULL, primary key with TeamName
\\\cline{2-5}
	& TeamName 
		& Unique identifier of the Research Team. 
		& Text
		& Foreign key to Research Team, Not NULL, primary key with ResID
\\\hline

\end{longtable}